---
title: Supplementary material for What do ecology and evolutionary biology journal websites communicate about their policies and preferences regarding replication studies?
author: Leyla Cabugos, Joel L. Pick, Marija Purgar
---




```{r, echo=FALSE, message=FALSE,warning=FALSE}

library(beeswarm)
library(viridis)
library(scales)

setwd("/Users/joelpick/github/replication_policy")

dd <- read.csv("./Data/replication_data.csv")
pub <- read.csv("./Data/publishers.csv")

dd$Publisher2<-pub$Publisher2[match(dd$Journal,pub$Journal)]

## remove out of scope papers
dd_scope <- subset(dd,info_found!="Out of scope for this journal")
dd_scope$JIF <- as.numeric(dd_scope$JIF)
dd_scope$JIF_log <- log(dd_scope$JIF)


# group replication policy and accepting categories into single variables
# dd_scope$replication_policy <- ifelse(dd_scope$info_found=="Yes", ifelse(dd_scope$replications_mention=="Yes",dd_scope$replication_policy_mentions,dd_scope$replication_policy_not),NA)

# pub_tab<-table(dd_scope$Publisher2,dd_scope$replication_policy)
#pub_tab[rowSums(pub_tab)>0,c(1,3,2,4)]
```


# Does accounting for publisher impact JIF analysis

In the main article, we modelled journal impact factor as a function of whether there was information on replication and whether novelty language was used. We do not account foe the potential non-independence between different publishers. 

This was suggested during peer review, and so here we present a sensitivity analysis, including a random effect of publisher. We test the statistical significance of the two predictors using likelihood ratio tests, comparing models with both predictors, with models that drop one predictor at a time. 

```{r, echo=FALSE, message=FALSE}

model_full<-lme4::lmer(JIF_log~novelty + info_found + (1|Publisher2),dd_scope )
model_noN<-lme4::lmer(JIF_log~info_found + (1|Publisher2),dd_scope )
model_noR<-lme4::lmer(JIF_log~novelty + (1|Publisher2),dd_scope )
anova(model_full,model_noN)
anova(model_full,model_noR)
summary(model_full)

model_noRE<-lm(JIF_log~novelty + info_found,dd_scope )
summary(model_noRE)
```

# Do impact factors vary between publishers

We can examine the variation among publishers

```{r, echo=FALSE, message=FALSE}

pub_tab<-table(dd_scope$Publisher2)
mult_pub<-names(pub_tab[pub_tab>1])
dd_scope$mult_pub<-as.factor(dd_scope$Publisher2 %in% mult_pub)
new_order <- with(dd_scope, reorder(Publisher2, JIF_log , median , na.rm=T))

par(mar=c(4,10,1,1))

boxplot(JIF~new_order,dd_scope, horizontal=TRUE, ylab="",  border=c(2,4)[as.factor((pub_tab>1)[levels(new_order)])], yaxt="n", log="x", range=0)
Map(axis, side=2, at=1:length(levels(new_order)), col.axis=c(2,4)[as.factor((pub_tab>1)[levels(new_order)])], labels=levels(new_order), cex.axis=0.3, las=1)


# boxplot(JIF_log~mult_pub,dd_scope, horizontal=TRUE, las=1)
```


# Does whether replication are mentioned vary between publishers

```{r, echo=FALSE, message=FALSE}

## whether info is found or not 
pub_tab2<-table(dd_scope$Publisher2,dd_scope$info_found)

# pub_tab2[pub_tab2[,2]>0,]
# pub_tab2[rowSums(pub_tab2)==1,]

mult_pub<-rownames(pub_tab2[rowSums(pub_tab2)>1,])
dd_scope$mult_pub<-dd_scope$Publisher2 %in% mult_pub

table(dd_scope$mult_pub,dd_scope$info_found)
```





# 


```{r, echo=FALSE, message=FALSE}



#with(dd_scope, tapply(JIF_log,list(mult_pub,info_found),mean))

#with(dd_scope, tapply(JIF_log,list(mult_pub,novelty),mean))




####################
##### Figure 2
##### Impact factor figure
####################


se<-function(x)sd(x)/sqrt(length(x))

info_mean<-aggregate(JIF~info_found+mult_pub,dd_scope,mean)
info_se<-aggregate(JIF~info_found+mult_pub,dd_scope,se)

novelty_mean<-aggregate(JIF~novelty+mult_pub,dd_scope,mean)
novelty_se<-aggregate(JIF~novelty+mult_pub,dd_scope,se)



par(mfrow=c(1,2), mar=c(5,5,1,1))
beeswarm(JIF~info_found+mult_pub,dd_scope, subset=info_found!="Out of scope for this journal",pch=19, cex=0.75, col=scales::alpha(1,0.3),method = "compactswarm",corral="wrap", xlab="Information about replication", log=TRUE, at=4:1, ylab="Journal impact factor")
points(info_mean[,3]~c(4,2,1), pch=19, col="red")
arrows(c(4,2,1),info_mean[,3]+info_se[,3],c(4,2,1),info_mean[,3]-info_se[,3], code=3, angle=90, length=0.1, col="red")
mtext("A)",side=3, adj=0.02, las=1,outer=TRUE, line=-2, cex=1.5)

beeswarm(JIF~novelty+mult_pub,dd_scope, subset=novelty!="Out of scope for this journal",pch=19, cex=0.75, col=scales::alpha(1,0.3),method = "compactswarm",corral="wrap", xlab="Used novelty language", log=TRUE, at=4:1, ylab="Journal impact factor")
points(novelty_mean[,3]~c(4:1), pch=19, col="red")
arrows(c(4:1),novelty_mean[,3]+novelty_se[,3],c(4:1),novelty_mean[,3]-novelty_se[,3], code=3, angle=90, length=0.1, col="red")
mtext("B)",side=3, adj=0.53, las=1,outer=TRUE, line=-2, cex=1.5)



```

