---
title: Supplementary material for What do ecology and evolutionary biology journal websites communicate about their policies and preferences regarding replication studies?
author: Leyla Cabugos, Joel L. Pick, Marija Purgar
---

```{r setup_fig, include=FALSE}
knitr::opts_chunk$set(
  fig.path = "",
  cache = TRUE
  )
```


```{r, echo=FALSE, message=FALSE,warning=FALSE}

library(beeswarm)
library(viridis)
library(scales)

setwd("/Users/joelpick/github/replication_policy")

dd <- read.csv("./Data/replication_data.csv")
pub <- read.csv("./Data/publishers.csv")

dd$Publisher2<-pub$Publisher2[match(dd$Journal,pub$Journal)]

## remove out of scope papers
dd_scope <- subset(dd,info_found!="Out of scope for this journal")
dd_scope$JIF <- as.numeric(dd_scope$JIF)
dd_scope$JIF_log <- log(dd_scope$JIF)


# group replication policy and accepting categories into single variables
# dd_scope$replication_policy <- ifelse(dd_scope$info_found=="Yes", ifelse(dd_scope$replications_mention=="Yes",dd_scope$replication_policy_mentions,dd_scope$replication_policy_not),NA)

# pub_tab<-table(dd_scope$Publisher2,dd_scope$replication_policy)
#pub_tab[rowSums(pub_tab)>0,c(1,3,2,4)]
```

# Supplementary Analyses

## Does accounting for publisher impact Journal Impact Factor analysis

In the main article, we modelled journal impact factor as a function of whether there was information on replication and whether novelty language was used. We decided in our pre-registration to not account for the potential non-independence between different publishers. 

During peer review, it was suggested that we account for publisher effects, and so here we present a sensitivity analysis, including a random effect of publisher using the lme4 R package (version 1.1-37). We test the statistical significance of the two predictors using likelihood ratio tests, comparing models with both predictors, with models that drop one predictor at a time. 

Table SThe direction and statistical support for the two effects remain the same, but the coefficients (including the intercept) do change. This is because the number of journals per publisher is variable, and so this model represents the effects when balanced across publishers.

```{r, echo=FALSE, message=FALSE}

model_full<-lme4::lmer(JIF_log~novelty + info_found + (1|Publisher2),dd_scope )
model_noN<-lme4::lmer(JIF_log~info_found + (1|Publisher2),dd_scope )
model_noR<-lme4::lmer(JIF_log~novelty + (1|Publisher2),dd_scope )
novelty_test<-anova(model_full,model_noN)
rep_info_test<-anova(model_full,model_noR)

rbind(
cbind(summary(model_full)$coef[,1:2],
	rbind(NA,novelty_test[2,c("Chisq","Pr(>Chisq)")],rep_info_test[2,c("Chisq","Pr(>Chisq)")])
),
publisher=c(as.numeric(summary(model_full)$varcor),NA,NA,NA),
residual=c(summary(model_full)$sigma^2,NA,NA,NA)
)

model_noRE<-lm(JIF_log~novelty + info_found,dd_scope )
rbind(summary(model_noRE)$coef,
	residual=c(summary(model_noRE)$sigma^2,NA,NA,NA))

```


# Do impact factors vary between publishers

From the model above we can see that impact factors appears to vary among publishers. When we examine this, we can see that there is some distinction in the impact factor among between publishers with one journal (in red) and those with multiple (on blue)

```{r, echo=FALSE, message=FALSE}

pub_tab<-table(dd_scope$Publisher2)
mult_pub<-names(pub_tab[pub_tab>1])
mult_pub2<-names(pub_tab[pub_tab>5])
dd_scope$mult_pub<-as.factor(dd_scope$Publisher2 %in% mult_pub + dd_scope$Publisher2 %in% mult_pub2)
new_order <- with(dd_scope, reorder(Publisher2, JIF_log , median , na.rm=T))

par(mar=c(4,10,1,1))

boxplot(JIF~new_order,dd_scope, horizontal=TRUE, ylab="",  border=c(2,"purple",4)[as.factor(((pub_tab>1 )+( pub_tab>5))[levels(new_order)])], yaxt="n", log="x", range=0)
Map(axis, side=2, at=1:length(levels(new_order)), col.axis=c(2,"purple",4)[as.factor(((pub_tab>1 )+( pub_tab>5))[levels(new_order)])], labels=levels(new_order), cex.axis=0.3, las=1)
legend("bottomright",c("1","2-5",">5"),col=c(2,"purple",4),pch=19, title="Number of Journals", bty="n")

# boxplot(JIF_log~mult_pub,dd_scope, horizontal=TRUE, las=1)
```


# Does whether replication are mentioned vary between publishers

```{r, echo=FALSE, message=FALSE}

## whether info is found or not 
pub_tab2<-table(dd_scope$Publisher2,dd_scope$info_found)

# plot(table(table(dd_scope$Publisher2)))

# plot(as.numeric(tapply(dd_scope$info_found=="Yes",dd_scope$Publisher2,mean))~as.numeric(table(dd_scope$Publisher2)), log="x")

# plot(as.numeric(tapply(dd_scope$JIF,dd_scope$Publisher2,mean))~as.numeric(table(dd_scope$Publisher2)), log="xy")


# cor(log(as.numeric(tapply(dd_scope$JIF,dd_scope$Publisher2,mean))),log(as.numeric(table(dd_scope$Publisher2))))

# pub_tab2[pub_tab2[,2]>0,]
# pub_tab2[rowSums(pub_tab2)==1,]

# mult_pub<-rownames(pub_tab2[rowSums(pub_tab2)>1,])
# dd_scope$mult_pub<-dd_scope$Publisher2 %in% mult_pub

table(dd_scope$mult_pub,dd_scope$info_found)
barplot(t(table(dd_scope$mult_pub,dd_scope$info_found))[2:1,], beside=TRUE, names.arg=c("1 journal", "2-5 journals", ">5 journals"))

# nov<-table(dd_scope$mult_pub,dd_scope$novelty)
# nov[,2]/rowSums(nov)


```





# 


```{r, echo=FALSE, message=FALSE}



#with(dd_scope, tapply(JIF_log,list(mult_pub,info_found),mean))

#with(dd_scope, tapply(JIF_log,list(mult_pub,novelty),mean))




####################
##### Figure 2
##### Impact factor figure
####################


se<-function(x)sd(x)/sqrt(length(x))

info_mean<-aggregate(JIF~info_found+mult_pub,dd_scope,mean)
info_se<-aggregate(JIF~info_found+mult_pub,dd_scope,se)

novelty_mean<-aggregate(JIF~novelty+mult_pub,dd_scope,mean)
novelty_se<-aggregate(JIF~novelty+mult_pub,dd_scope,se)



par(mfrow=c(1,2), mar=c(5,5,1,1))
beeswarm(JIF~info_found+mult_pub,dd_scope, subset=info_found!="Out of scope for this journal",pch=19, cex=0.75, col=scales::alpha(1,0.3),method = "compactswarm",corral="wrap", xlab="Information about replication", log=TRUE, at=6:1, ylab="Journal impact factor")
points(info_mean[,3]~c(6,4:1), pch=19, col="red")
arrows(c(6,4:1),info_mean[,3]+info_se[,3],c(6,4:1),info_mean[,3]-info_se[,3], code=3, angle=90, length=0.1, col="red")
mtext("A)",side=3, adj=0.02, las=1,outer=TRUE, line=-2, cex=1.5)

beeswarm(JIF~novelty+mult_pub,dd_scope, subset=novelty!="Out of scope for this journal",pch=19, cex=0.75, col=scales::alpha(1,0.3),method = "compactswarm",corral="wrap", xlab="Used novelty language", log=TRUE, at=6:1, ylab="Journal impact factor")
points(novelty_mean[,3]~c(6:1), pch=19, col="red")
arrows(c(6:1),novelty_mean[,3]+novelty_se[,3],c(6:1),novelty_mean[,3]-novelty_se[,3], code=3, angle=90, length=0.1, col="red")
mtext("B)",side=3, adj=0.53, las=1,outer=TRUE, line=-2, cex=1.5)



```

